Bathtub Qualitative Reasoning

### 2016-10-21 paper.tex
removed transition to self

\section{Algorithm}

\begin{algorithm}
\If{condition}{then-block}
\caption{}
\end{algorithm}

@@

\begin{figure}[H]\label{state-graph}
\centering
\includegraphics[width=\textwidth, angle=90]{result.png}
\caption{Plot of the state-graph}
\end{figure}

>>>>

\section{Algorithm}
The goal of the algorithm is to construct a state graph based for a specific model and a given starting state. Constructing the state-graph is done iteratively as shown in Algorithm~\ref{alg:computing_state_graph}.
\begin{algorithm}
    result = \{"state": starting\_state, "children": [ ]\}

    processing\_list = [starting\_state]

\While{processing\_list not empty}{
    processing\_state = pop(processing\_list)

    successors = findSuccessors(processing\_state)

    \For{s in succesors}{
        \If{s not in result}{
            add s to result

            add s to processing\_list
        }
        add s as child to processing\_state
    }
}
\caption{Computing the state-graph based on given an starting state. It starts with a given starting state in the processing list, then it computes all the successors of this state and adds all the succesors as children to state that is being processed, as well as adding these succesors to the processing list, but only if a successor was not already processed.}
\label{alg:computing_state_graph}
\end{algorithm}

The core functionality of constructing the state graph is encapsulated in finding all successive states for a given state. The first step in finding the successive states, is propagating over all quantities in the model and computing all possible combinations of new values based on the derivatives. The algorithm for doing this is shown in Algorithm~\ref{alg:propogating_values}.
\begin{algorithm}
new\_states = [ empty\_state ]

    \For{quantity in quantities}{

        p = possible next values for quantity\\
        \ForAll{new\_states}{
            new\_state = pop(new\_states)\\
            \ForAll{p}{
               add new\_state with new possible value for quantity to new\_states
            }
        }
        }
\caption{Propagate over all quantities and modify value based on the derivative. This is done by looping over all quantities in the model and computing all the possible values for a next state based on its current value and its derivative. For each possible next value we create a new state, thus possibly creating multiple states. Because, we can have new states created by value splits of previous quantities, we need to create new states for each state that was created previously}
\label{alg:propogating_values}
\end{algorithm}

After computing all the possible successive states only with respect to the values, the algorithm performs a check whether all value constraints hold and removes the state if a state does not satisfy all value constraints.

The next step in the algorithm is to determine new derivatives based on the influences.
\begin{algorithm}

\For{quantity in quantities}{

    \If{quantity has influences} {
        \ForAll{influences on quantity}{
            new\_state = pop(new\_states)\\
            \ForAll{p}{
               add new\_state with new possible value for quantity to new\_states
            }
        }

    }
}
\caption{}
\label{alg:propogating_influences}
\end{algorithm}

@@

\begin{figure}[H]\label{state-graph}
\centering
\includegraphics[width=\textwidth]{result.png}
\caption{Plot of the state-graph}
\end{figure}
